\section{Budget Justification}
This proposed budget is for 36 months. Salary for all named personnel was calculated based on the actual budgeted Texas A\&M University (TAMU) salary.  Fringe benefits have been calculated according to standard rates.  A 3\% salary escalation per year has been included.

\subsection{Senior Personnel}
Principal Investigator, Aleksei Zheltikov, Ph.D., (Rate of pay \$21,687, effort 0.30 calendar months) will be responsible for overall coordination, including experiments, data analysis and interpretations, manuscript production, conference presentations, and reports as required.

\subsection{Other Personnel}
Postdoctoral Research Assistant, to be named, Ph.D.: (Rate of pay \$77,273, effort 6 calendar months) will work under the direction of Dr. Aleksei Zheltikov, will function as project manager, will participate in all stages of experimental work, theoretical analysis including analytical calculations, data analysis, and manuscript preparation.  This postdoctoral researcher will also mentor graduate research assistants and present results of this research at scientific meetings.

\subsection{Capital Equipment}
Capital equipment expenditures will include: a high dynamic range camera (Cost: \$17,000) necessary for sensitive 
imaging of fluorescent output of NVDs in super-resolution measurements and for simultaneously measuring small 
changes in fluorescence signal output from multiple channels of fiber nitrogen—vacancy diamond probes, a lock-in 
amplifier (Cost: \$9,000) necessary to facilitate lock-in detection enhanced signal to noise ratio in all 
measurement regimes, and a vector network analyzer (Cost: \$25,000) necessary to characterize and optimize the 
performance of the microcircuitry delivering microwave excitation to nitrogen—vacancy centers for improved signal 
to noise ratios and optimized probe geometry for biocompatibility.

\subsection{Other Direct Costs}
Materials and Supplies include optical components, translation stages, safety equipment, electronic test equipment, 
and optomechanical hardware necessary for the experimental setup, as well as computer peripheral hardware.

\subsection{Indirect Costs}
Indirect costs are calculated at the Texas A\&M University, Department of Health and Human Services (DHHS) 
negotiated rate of 48.5\% of MTDC.